Supplementary Material for ``Evaluating infectious disease forecasts with allocation scoring rules''

### 2023-12-10 alloscore_manuscript/supplement.rnw
a few more edits in sec:distfromq_alloscore_proper_prospective

We consider a setting where a forecasting exercise (such as a forecast hub) pre-specifies that forecasts will be represented using a parametric family of forecast distributions $F_\theta(y)$, and forecasts will be specified by providing the value of the parameters $\theta$. We use $\mathcal{P}$ to denote the collection of all distributions $F_\theta$ in the given parametric family. For instance, it has recently been proposed that mixture distributions could be used to represent forecast distributions \cite{wadsworth2023mixture}. Additionally, we note that the functionality in \verb`distfromq` can be viewed as specifying a parametric family of distributions where the parameters $\theta$ are given the interpretation of being the quantiles of $F_\theta$ at pre-specified probability levels, but more generally control the shape of $F_\theta$ over the full range of its support.

>>>>

We consider a setting where a forecasting exercise (such as a forecast hub) pre-specifies that forecasts will be represented using a parametric family of forecast distributions $F_\theta(y)$, and the task of the forecaster is to select a particular parameter value $\theta$. We use $\mathcal{P}$ to denote the collection of all distributions $F_\theta$ in the given parametric family. For instance, it has recently been proposed that mixture distributions could be used to represent forecast distributions \cite{wadsworth2023mixture}. Additionally, we note that the functionality in \verb`distfromq` can be viewed as specifying a parametric family $\mathcal{P}_{\mathrm{dfq}}$ where the parameters $\theta$ of $F_\theta$
are its quantiles at pre-specified probability levels, and where the shape of any $F_\theta \in \mathcal{P}_{\mathrm{dfq}}$ over the full range of its support is entirely controlled by these quantiles.
